\section*{Relational Algebra Operations}

\vspace{-0.1cm}

\begin{center}
\noindent
\textit{Students Table:} ID, Name, Age, Major. \\
\textit{Courses Table:} CourseID, Name, Credits.
\end{center}


\vspace{-0.7cm}
\subsection*{Basic Operations}
\vspace{-0.1cm}

\begin{itemize}[noitemsep,leftmargin=*]
\leftskip-\dimexpr\leftmargin %%%

% Select
\item[]{\textbf{Select} $(\sigma)$:
$\sigma_{\text{Age} > 21}(\text{Students})$. \\
Selects rows where age larger than 21 years.}

% Project
\item[]{\textbf{Project} $(\pi)$:
$\pi_{\text{Name, Major}}(\text{Students})$. \\
Selects the `Name` and `Major` columns from the `Students` table.}

% Union
\item[]{\textbf{Union} $(\cup)$:
$\pi_{\text{Name}}(\text{Students}) \cup \pi_{\text{Name}}(\text{Courses})$. \\
Combines the `Name` columns from `Students` and `Courses` tables.}

% Set Difference
\item[]{\textbf{Set Difference} $(-)$:
$\pi_{\text{Name}}(\text{Students}) - \pi_{\text{Name}}(\text{Courses})$. \\
Rows in the first relation (Students) but not in the second (Courses).}

% Cartesian Product
\item[]{\textbf{Cartesian Product} $(\times)$:
$\text{Students}_1 \times \text{Courses}_2$. \\
Creates pairs of every student with every course. Every $item_1$ goes with every $item_2$.}

% Rename
\item[]{\textbf{Rename} $(\rho)$:
$\rho_{\text{Pupils}(\text{ID, StudentName, StudentAge, Major})}(\text{Students})$. \\
Renames the `Students` table to `Pupils` and its attributes accordingly.}

% Intersection
\item[]{\textbf{Intersection} $(\cap)$:
$\pi_{\text{Name}}(\text{Students}) \cap \pi_{\text{Name}}(\text{Courses})$. \\
Finds names common to both `Students` and `Courses`.}

% Natural Join
\item[]{\textbf{Natural Join} $(\bowtie)$:
$\text{Students} \bowtie \text{Enrollments}$. \\
Joins `Students` and `Enrollments` on common attributes/columns.}

% Theta Join
\item[]{\textbf{Theta Join}:
$\text{Students} \bowtie_{\text{Students.Major = Courses.Name}} \text{Courses}$. \\
Joins `Students` and `Courses` where the student's major matches the course name.}

% Division
\item[]{\textbf{Division}:
$\text{Enrollments} \div \pi_{\text{CourseID}}(\sigma_{\text{Instructor = 'Dr. Smith'}}(\text{Courses}))$. \\
Finds students who are enrolled in all courses taught by 'Dr. Smith'.}


\item[]{\textbf{Projection, Join, Selection}: \\
$\pi_{\text{StudentName, CourseName}} (\sigma_{\text{Age} > 21} (\text{Students} \bowtie \text{Enrollments} \bowtie \text{Courses}))$ \\
Retrieves names of students older than 21 and their course names.}

\item[]{\textbf{Union and Intersection}: \\
\vspace{-0.2cm}
\begin{center}
$\left( \pi_{\text{Name}} (\sigma_{\text{Major} = 'CS'}(\text{Students})) \cup \pi_{\text{Name}} (\sigma_{\text{Age} > 21}(\text{Students})) \right) -  \left( \pi_{\text{Name}} (\sigma_{\text{Major} = 'CS'}(\text{Students})) \cap \pi_{\text{Name}} (\sigma_{\text{Age} > 21}(\text{Students})) \right)$ \\
\end{center}
Finds students either majoring in CS or older than 21, excluding those who meet both criteria.}

\item[]{\textbf{Nested Operations}: \\
$\pi_{\text{InstructorName}} (\sigma_{\text{CourseName} = 'Math'}(\text{Courses})) - \pi_{\text{InstructorName}} (\sigma_{\text{CourseName} = 'Physics'}(\text{Courses}))$ \\
Identifies instructors teaching 'Math' but not 'Physics'.}

\end{itemize}
